Untitled

### 2019-05-28 manuscript/manuscript draft.Rmd
Update manuscript draft.Rmd

### Methods
1.	ForC database [@Anderson-Teixeira2018]
+ Used data compiled from existing literature
2.	Climate data
+	WorldClim [@Hijmans2005]; WorldClim 2: vapour pressure and solar radiation [@Fick2017]
+	CRU: cloud cover; annual frost days; potential evapotranspiration; annual wet days [@Harris2014]
+	Global Aridity Index and Potential Evapotranspiration Climate Database [@Trabucco2018]
+	TerraClimate: vapour pressure deficit [@Abatzoglou2018]
3.	Run models in R

>>>>

### Methods  
1.	ForC database [@Anderson-Teixeira2018]
+ Used data compiled from existing literature
+ 
2.	Climate data
+	WorldClim [@Hijmans2005]; WorldClim 2: vapour pressure and solar radiation [@Fick2017]
+	CRU: cloud cover; annual frost days; potential evapotranspiration; annual wet days [@Harris2014]
+	Global Aridity Index and Potential Evapotranspiration Climate Database [@Trabucco2018]
+	TerraClimate: vapour pressure deficit [@Abatzoglou2018]
3.	Run models in R
+ Model specification: mixed model using the lme4 package in R. 
+ Model = response_variable ~ fixed_variable + altitude + (1/geographic_area/plot_name), weighted by koeppen climate area

#### Database  
Analyses were conducted on data contained in the open-access ForC database [@Anderson-Teixeira2016; @Anderson-Teixeira2018]. This database contains records of field-based measurements of forest carbon stocks and annual fluxes, compiled from previously published studies and existing databases (e.g. ORNL DAAC; Luyssaert etc?).  
*Data selection.* ForC contains measures of carbon stocks and fluxes; for the purposes of this analysis only measures of primary productivity were selected from the database. The variables selected were: GPP, NPP, BNPP (total root and fine root), ANPP (total ANPP, foliage, wood and woody stem).  
Sites were excluded from analysis if they were managed, defined as plots that were planted, managed as plantations, irrigated, fertilised or including the term "managed" in their site description. Sites that had experienced significant disturbance were also excluded. Disturbances that justified site exclusion were major cutting or harvesting, and/or burning, flooding, drought and storm events with site mortality >10% of trees.  
There is evidence that stand age influences patterns of primary productivity and carbon allocation in forest ecosystems [@DeLucia2007; @Gillman2015]. To reduce any biasing effects of stand age, stands under 100 years of age were excluded from analysis.
